MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-20 ms.tex
Added more references to the intro

% Gravitational lensing as a geometric (?) test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  In particular, the
deep gravitational potential wells of galaxy clusters provide a strong
lens, with lensed images that can be seen by eye.  Strong
gravitational lensing can manifest as visible giant arcs magnifying
high redshift galaxies \citep{lyndsandpetrosian_86,gladders_??},
multiply imaged quasars \citep{walsh_etal79}, and arclets.  Lensing
signatures probe the underlying dark matter distribution of galaxy
clusters \citep{warrenanddye_03}, probe high redshift galaxy formation
\citep{allam_etal07}, and provide a geometric test of cosmology.

% Arc identification can be done visually (e.g. that zooniverse
% thing).  But, in the advent of optical surveys, DES and LSST, we
% will be limited by our ability to automatically process the large
% amounts of data.  Wide field surveys - SPT in millimeter, Herschel
% in submillimeter; high resolution spectroscopic imaging with ALMA;
% optical surveys DES, HSC, LSST, and Euclid (Oguri \& Marshall 2010).
The geometric test of cosmology requires a comparison of predicted arc
abundances and observed abundances
\citep{kochanek_96,chae_02,linder_04}.  Visual arc identification has
been effective through the use of citizen science platforms
(e.g. \citet{marshall_etal16,more_etal16}).  However, in the advent of
large surveys, such as the Dark Energy Survey (DES) and the Large
Synoptic Sky Telescope (LSST), we will be limited by our ability to
automatically process large amounts of data and select likely strong
lensing clusters for follow up visual and spectroscopic confirmation.
The strong lensing sector of cluster-based cosmology requires an
exploration of techniques in image processing and classification.

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure has emerged for both large scale
visual and automated image classification. By nature, the human eye is
one of the best discriminators for image classification.  {\em
  SpaceWarps} is an example of citizen science based image
classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  Visual classification has been
quite successful for a dataset like CFHTLS, classifying \change{XX in
  XX time}.  However, future datasets like Euclid and LSST will be
\change{XX} times this size, challenging the scalability of a citizen
science approach.  The next step is to find automated methods with
performance comparable to or better than humans. {\em SpaceWarps} is a
part of the Zooniverse Project (CITE???), which also includes {\em
  Galaxy Zoo}, the citizen science based image classification of
galaxy types (CITE???).  Galaxy classification is a successful example
of in which machine learning algorithms successfully train models to
classify images with comparable performance to humans (CITE???).

% Describe general robot identification schemes that have been
% implemented
General automated, or ``robot'', identification refers to a classifier
where images are fed into an image processing pipeline that enhances
and extracts characteristic features as parameters on which a pattern
recognition piece is applied [wc???].  Examples of this include
ArcFinder ... .... \citep{seidelandbartelmann_07}. For multiply imaged
quasars, Ringfinder ... ... ...\citep{gavazzi_etal14}.  Each pipeline
.... ... and relies on the image morphology where ... ...  Note, that
the method best applied to ... ... and the objects of interest.

>>>>

% Gravitational lensing as a geometric (?) test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  In particular, the
deep gravitational potential wells of galaxy clusters provide a strong
lens, with lensed images that can be seen by eye.  Strong
gravitational lensing can manifest as visible giant arcs magnifying
high redshift galaxies \citep{lyndsandpetrosian_86,gladders_etal03},
multiply imaged quasars \citep{walsh_etal79}, and arclets.  Lensing
signatures probe the underlying dark matter distribution of galaxy
clusters \citep{warrenanddye_03}, probe high redshift galaxy formation
\citep{allam_etal07}, and provide a geometric test of cosmology via
comparison of predicted arc abundances and observed abundances
\citep{kochanek_96,chae_03,linder_04}.

% Arc identification can be done visually (e.g. that zooniverse
% thing).  But, in the advent of optical surveys, DES and LSST, we
% will be limited by our ability to automatically process the large
% amounts of data.  Wide field surveys - SPT in millimeter, Herschel
% in submillimeter; high resolution spectroscopic imaging with ALMA;
% optical surveys DES, HSC, LSST, and Euclid (Oguri \& Marshall 2010).
Visual arc identification has been effective through the use of
citizen science platforms (e.g. \citet{marshall_etal16,more_etal16}).
However, in the advent of large surveys, such as the Dark Energy
Survey (DES) and the Large Synoptic Sky Telescope (LSST), we will be
limited by our ability to automatically process large amounts of data
and select likely strong lensing clusters for follow up visual and
spectroscopic confirmation.  The strong lensing sector of
cluster-based cosmology requires an exploration of techniques in image
processing and classification.

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure has emerged for both large scale
visual and automated image classification. By nature, the human eye is
one of the best discriminators for image classification.  {\em
  SpaceWarps} is an example of citizen science based image
classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  Visual classification has been
quite successful for a dataset like CFHTLS, classifying \change{XX in
  XX time}.  However, future datasets like Euclid and LSST will be
\change{XX} times this size, challenging the scalability of a citizen
science approach.  The next step is to find automated methods with
performance comparable to or better than humans. {\em SpaceWarps} is a
part of the Zooniverse Project (CITE???), which also includes {\em
  Galaxy Zoo}, the citizen science based image classification of
galaxy types \citep{lintott_etal08}.  Galaxy classification is a
successful example of in which machine learning algorithms
successfully train models to classify images with comparable
performance to humans \citep{dieleman_etal15}.

% Describe general robot identification schemes that have been
% implemented
General automated, or ``robot'', identification refers to a classifier
where images are fed into an image processing pipeline that enhances
and extracts characteristic features as parameters on which a pattern
recognition piece is applied.  Examples of this include ArcFinder for
group or cluster scale lens \citep{seidelandbartelmann_07}, Ringfinder
for multiply imaged quasars\citep{gavazzi_etal14}, .  Each pipeline
.... ... and relies on the image morphology where ... ...  Note, that
the method best applied to ... ... and the objects of interest.
